---
title: "Motion Tracking"
author: "Nanna Bernth"
date: "4 apr 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/nanna/OneDrive - Aarhus universitet/4. Semester/Models of Perception and Action/Modelsofperception/Exercise Homework/21")
getwd()


library(pacman)
p_load(readr, tidyverse, reshape, mousetrap, mousetrack)


data <- list.files(pattern = "*.txt") %>% 
  lapply(read.delim, stringsAsFactors=F, sep=",", header=F) %>% 
   bind_rows

data <- rename(data, c(V1 = "sample", V2 = "condition", V3 = "pos_x", V4 = "pos_y"))

```

Mouse-tracking: like a histogram, taking a course without touching the pillars

Intention with experiment: 
	• Gauge the repetition effect
	• If deviation from the pattern (difference in height) --> longer RT
	• Remapping effect
	• If many tall pillars, and one low in the middle --> you would probably go a lot higher on the low one as you're used to the taller ones
		○ Cordula found this effect!
		○ Repetition --> it's cost-effective to just keep the previous pattern
	• If many low pillers, and one tall one in the middle --> you overestimate the sufficient movement
		○ The tall pillar is an obstacle 
The data is more mixed in this effect though

```{r}

#Make a table with a single trial (15)
single <- read.delim("21_15.txt", sep=",", header=F)
single <- rename(single, c(V1 = "sample", V2 = "condition", V3 = "pos_x", V4 = "pos_y"))

#Plot the data
ggplot(data = single, aes(x = pos_x, y = pos_y)) + geom_point(color = rainbow(2268), size = 0.4) 

```

```{r}

#Find minimum value in pos x and pos y
miny = min(single$pos_y)
minx = min(single$pos_x)

#Make a new column where the minimun value is subtracted the original values
single$pos_y0 <- single$pos_y - miny
single$pos_x0 <- single$pos_x - minx

#Plot the new data
ggplot(data = single, aes(x = pos_x0, y = pos_y0)) + geom_point(color = rainbow(2268), size = 0.4) 

```

```{r + Travel distance}

traveldist <- sum(sqrt(diff(single$pos_x0)^2 + diff(single$pos_y0)^2))
traveldist

#5523.131 the distance from start to end of trial the 'mouse' travels.

```

```{r + time column}

#Adding a time variable (+ 0.0025)
single$time <- (single$sample-1) * 0.0025

```


```{r}

#Velocity
single$velocity_y <- (single$pos_y0 - lag(single$pos_y0, 1)) / 0.0025

#Acceleration
single$acceleration_y <- (single$velocity_y - lag(single$velocity_y, 1)) / 0.0025



#Plot
ggplot(data = single, aes(x = time, y = acceleration_y)) + geom_point(color = rainbow(2268), size = 0.4)


ggplot(data = single, aes(x = time, y = velocity_y)) + geom_point(color = rainbow(2268), size = 0.4)


```


```{r}

p_load(rootSolve)

zero <- as.data.frame(uniroot.all(approxfun(single$time, single$acceleration_y), interval = range(single$time)))
zero

```




